---
title: "MyDepression Report"
author: "MyDepression Application"
date: 7/6/2017

output: html_document
---
<style> body{ font-family: 'Oxygen', sans-serif; font-size: 16px; line-height: 24px; } h1,h2,h3,h4 { font-family: 'Raleway', sans-serif; } .container { width: 1000px; } h3 { background-color: #D4DAEC; text-indent: 100px; } h4 { text-indent: 100px; } g-table-intro h4 { text-indent: 0px; } </style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo=FALSE, results='asis'}
cat("Test Date: ",clientlocaltime)
#format(Sys.time(), "%a %b %d %X %Y")
```
```{r echo=FALSE}
#library(shiny)
#HTML(oi[[1]])

```
 
### Results:

## 1- Depression Network Graph

This graph is computed based on the symptom severity scores and the causality matrix which you supplied in step 1 and 2 respectively.It represents the interplay of depressive symptoms in your case.

```{r  echo=FALSE}
library(qgraph)
qgraph(qgresult)
```

## 2- Centrality of symptoms

```{r echo=FALSE, results='asis'}


kable(oddf,caption="Outdegree Centrality",align=c("c"))
```


## 3- Symptom Severity 

```{r echo=FALSE, results='asis'}

 mscores=as.matrix(rv$scores)
colnames(mscores)=c("Score")
kable(mscores,caption="PHQ-9 Scores")
#dbphq<- read.csv("PHQ.csv",header=T)

```

## 4- Overall Severity
```{r echo=FALSE, results='asis'}
totalscore<-sum(as.numeric(rv$scores))
rownumber=which(apply(dbphq,1,function(x){totalscore %in% eval(parse(text=x[[1]]))})==TRUE)
cat(paste0("Based on the abobe-mentioned scores your total score is ",bold(totalscore)," ,which translates to a severity of ",bold(dbphq[rownumber,2]),".Based on this score, PHQ-9 suggests the following course of action : ",bold(dbphq[rownumber,3]) )) 
```


### Explanation:

In the above graph each symptoms is represented by a circles or technical term a "node". The relationship between these nodes are represented by arrows. For example if "a" and "b" are two symptoms; a->b means symptom a contributes to symptom "b".In other terms, as symptom "a" score increases, an increase in symptom b ensues. Unless there is a reverse arrow (b->a), symptom b does not contribute to worsening of symptom "a". In other terms based on the data you supplied there is a causal dependence of symptom "b" on symptom "a".

Each person's depression is unique in terms of interplay of symptoms and the resulting clinical picuture and importatantly, this graph uniquely represents your depression.

The severity score of each symptom which you supplied in the first table, is represented by the shade of the color of that symptom's node. so for example if you scored a symptom as happening "Nearly every day", the color of the circle would be deep red and if a symptom is scored as "Not at all", the color is a much lighter shade of red. 

But this is not all the story that the graph tells. More information is calculated and condensed visually in the graph. For example, the size of a node reflects its "Centrality". Centrality is a group of indices which are calculated by the software for each node based on degreeof interaction of that node with other nodes in the network. Well established statystical formula defined in the software compute these measures. But to avoid the technical jargon, in its simplest form "Centrality" of a symptom is defined as its "importance" in the network, overall. Based on these values, the software actually assigns a more central position to central symptoms. This isdone by implementing a "Layout Algorhythm". In other terms, symptoms that are bigger in size are placed more central in the graph. 

But what is the importance of Centrality and the network graph that is rendered based on it for you, the patient. Even though these calculations and measures are a magnet for researchers in the field like me, they are not the reason behind designing MyDepression. The goal of designing myDepression is

1- to help patient benefit directly from the network analysis approach by offering him/her personalized data and graphs and then data-driven conclusions based on them. These data serve two purpose:
      a) imporve the patient's understanding of characteristics of his/her own disease and interplay of its symptoms. Therefore he is now not solely limited to the results of empiric trials researching depression in hundreds or tousand patients and presenting the cumulative data as results. In other terms MyDepression graph and other data are "individualized of the patient.
      b)More importantly, MyDepression results could serve as a roadmap for the care provider to  target the more important(central) symptoms and achieve better therapeutic response. 
      c)The analysis takes a few minutes. Results are saved and accessible to download or email. To get the most out of MyDepression we suggeste repeated analysis in regular intervals to assess the effect of treatment quantitatively. A positive effect will show as decreased centrality(or size of the circle) of the targeted node as well as lighter shades of color of the circle which is in essence a reflection of severity of the specific symptom.

Acutually myDepression yields several different measures of Centrality for each symptom. All the measures are attached at the end of the report for those patoients and providers who are eager to delve deeper into the realm of network analysis in depression 

But here we focus on "Degree Centrality" and more specifically "OutDegree Centrality of each symptom". Outdegree Centrality, is the number of arrows which originate from a node. If a lot of arrows originate from a symptom,this means it is a symptom that contribute to worsening of many other symptoms in the graph. How are we going to use this data to individualize treatment. Simple, we would target that specific symptom with high Outdegree Centricity and the resuplt would logically be improvement of the symptoms toward which the arrows point. This in turn improves the overall severity of depression in a more prominant manner. 

#  Causality Matrix


```{r echo=FALSE, results='asis'}

 kable(m2numeric,caption="Causality Matrix",align=c("c")) 

```